---
title: "Some Ideas for Using imageR"
author: "Kent Russell"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Some Ideas for Using imageR}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

`imageR` enlivens your images and plots from `R`.  As an htmlwidget, it works in all contexts with nearly all types of HTML elements.  While there are lots of great JavaScript image libraries, `imageR` will begin its life with a wrapper for [intense-images](http://tholman.com/) by the talented, creative, and funny [Tim Holman](http://tholman.com/).  I know humor is subjective, but test my definition of "funny" with Tim's [giflinks](http://tholman.com/giflinks/).

Let's see a couple of ways we might use `imageR`.  Please don't let my lack of creativity hamper you.  Experiment, play, use, and share.  **Yes, it works on touch devices** and is responsive, so try it on that little device in your pocket or purse.

### Quick Installation

`imageR` has not stabilized enough for CRAN, so for now please install with `devtools::install_github`.

```{r eval = F}
devtools::intall_github("timelyportfolio/imageR")
```

### Simple Example

I say this is simple, but getting the image right will require use of `base64` encoding, which might be new to you.  `base64` might sound hard, but fortunately, two packages `base64enc` (which we'll use) and `base64` make it easy.

```{r "example_01"}
library(imageR)
library(htmltools)
library(base64enc)

# ignore the local if it confuses you
# only use it to delete the tempfile on exit
local({
  # make a tempfile to hold our chart  
  tf <- tempfile()
  # delete our tempfile on exit
  on.exit(unlink(tf))
  
  # save our chart as a big png; exaggerate the width
  png( tf, height = 800, width = 1600 )
    # make a kind of pretty chart
    plot(sin(0:90),cos(seq(0,360,by=4)),type="l", col= topo.colors(4))
    lines(sin(0:90),cos(0:90),type="l",col=topo.colors(4)[3])
  dev.off()
  
  intense(
    tags$img(
      style="height:200px;"
      ,src = dataURI(file=tf,mime="image/png")
    )
    ,height = 200
  )
})
```

### Example with Pairs to Show Auto

In the first example, we exaggerated the width so you could see how the image pans from right to left based on your mouse or touch movement.  `intense-images` automatically decides to pan.  To see how it adjusts resize your window when in full-screen display mode.

```{r "example_02"}
library(imageR)
library(htmltools)
library(base64enc)

# ignore the local if it confuses you
# only use it to delete the tempfile on exit
local({
  # make a tempfile to hold our chart  
  tf <- tempfile()
  # delete our tempfile on exit
  on.exit(unlink(tf))
  
  # save our chart as a big png
  png( tf, height = 1200, width = 1200 )
    # make a kind of pretty chart
    pairs(USJudgeRatings, main="Example from ?pairs")
  dev.off()
  
  intense(
    tags$img(
      style="height:400px;overflow:hidden;"
      ,src = dataURI(file=tf,mime="image/png")
    )
    ,height = 400
  )
})
```

### Example with a Non-`img`

`intense-images` also works with non-`img` elements, such as a `div`.  To make it work correctly, we'll use some extra tag attributes `data-image`, `data-title`, and `data-caption` on our non-`img`.  I bet you can guess what these attributes mean.  We'll use the same plot with some different colors as above to illustrate the difference.

```{r "example_03"}
library(imageR)
library(htmltools)
library(base64enc)

# ignore the local if it confuses you
# only use it to delete the tempfile on exit
local({
  # make a tempfile to hold our chart  
  tf <- tempfile()
  tf2 <- tempfile()
  # delete our tempfile on exit
  on.exit({unlink(tf);unlink(tf2)})

  png( tf, height = 1200, width = 1200 )
    # make a kind of pretty chart
    pairs(USJudgeRatings, main="Example from ?pairs")
  dev.off()
  
  # save our chart as a smaller png than above for demo
  png( tf2, height = 800, width = 800 )
    # make a kind of pretty chart
    pairs(USJudgeRatings, main="Example from ?pairs",
      pch = 4, col="blue", cex = 0.5
    )
  dev.off()
  
  tagList(
    intense(
      # method already shown
      tags$img(
        style="height:200px;width:200px;overflow:hidden"
        ,src = dataURI(file=tf,mime="image/png")
      )
      ,height=250, width = 400
    )
    , intense(
      tags$div(
        "data-image" = dataURI(file=tf2,mime="image/png")
        ,"data-title" = "?pairs example"
        ,"data-caption" = "neat things happen with extra attributes"
        ,style = "height:50px;width:250px;border: dashed 0.2em lightgray;"
        ,"not an img but still intense; click me"
      )
      ,height = 250, width = 50
    )
  )
})
```

### With Other htmlwidgets and Flickr

htmlwidgets are composeable.  Let's add `intense-images` to an example from [Week 10 | Responsive Toolbars](http://www.buildingwidgets.com/blog/2015/3/11/week-10-responsive-toolbars) with `navr` and `sortableR`.  You might say this is more like publishing with HTML, and you are right.  R is really not necessary for this example, but when you are in a context, it is often much more efficient to stay in that context.  Thanks

```{r "example_04"}
library(htmltools)
library(curl)
library(navr)
library(sortableR)
library(imageR)

n1 <- navr(
  selector = "#sortableR-toolbar"
  ,taglist = tagList(
    tags$ul(id = "sort-navr"
      ,style="line-height:120px; text-align:center; vertical-align:middle;"
      ,tags$li(
        style="border: solid 0.1em white;border-radius:100%;line-height:inherit;width:130px;height:130px;"
        , class="fa fa-binoculars fa-4x"
        #  attribution everywhere Creative Commons Flickr
        #  awesome picture by https://www.flickr.com/photos/12859033@N00/2288766662/
        , "data-image" = paste0(
          "data:image/jpg;base64,"
          ,base64enc::base64encode(
            curl("https://farm4.staticflickr.com/3133/2288766662_c40c168b76_o.jpg","rb")
          )
        )
        , "data-title" = "Binoculars, a working collection"
        , "data-caption" = "awesome picture courtesy Flickr Creative Commons
            <a href = 'https://www.flickr.com/photos/12859033@N00/2288766662/'>jlcwalker</a>"
      )        
      ,tags$li(
        style="border: solid 0.1em white;border-radius:100%;line-height:inherit;width:130px;height:130px;"
        , class="fa fa-camera fa-4x"
        #  attribution everywhere Creative Commons Flickr
        #  awesome picture by https://www.flickr.com/photos/s58y/5607717791
        , "data-image" = paste0(
          "data:image/jpg;base64,"
          ,base64enc::base64encode(
            curl("https://farm6.staticflickr.com/5309/5607717791_b030229247_o.jpg","rb")
          )
        )
        , "data-title" = "Leica IIIc converted to IIIf BD ST"
        , "data-caption" = "awesome picture courtesy Flickr Creative Commons
            <a href = 'https://www.flickr.com/photos/s58y/5607717791'>s58y</a>"
      )
    )
  )
)

tagList(
  tags$div(
    id = "sortableR-toolbar"
    ,style="width:300px;border: dashed 0.2em lightgray; float:left;"
    ,tags$h3("sortableR Icons for Intense Images")
    ,"These icons drag and drop. Click on them for an"
    ,tags$strong("intense")
    ,"result."
  )
  ,add_font_awesome(n1)
  ,sortableR("sort-navr")
  ,intense( selector = "#sort-navr li" )
)
```
