---
title: "Some Ideas for Using imageR"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Some Ideas for Using imageR}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

`imageR` enlivens your images and plots from `R`.  As an htmlwidget, it works in all contexts with nearly all types of HTML elements.  While there are lots of great JavaScript image libraries, `imageR` will begin its life with a wrapper for [intense-images](http://tholman.com/) by the talented, creative, and funny [Tim Holman](http://tholman.com/).  I know humor is subjective, but test my definition of "funny" with Tim's [giflinks](http://tholman.com/giflinks/).

Let's see a couple of ways we might use `imageR`.  Please don't let my lack of creativity hamper you.  Experiment, play, use, and share.  **Yes, it works on touch.**

### Quick Installation

`imageR` has not stabilized enough for CRAN, so for now please install with `devtools::install_github`.

```{r eval = F}
devtools::intall_github("timelyportfolio/imageR")
```

### Simple Example

I say this is simple, but getting the image right will require use of `base64` encoding, which might be new to you.  `base64` might sound hard, but fortunately, two packages `base64enc` (which we'll use) and `base64` make it easy.

```{r "example_01"}
library(imageR)
library(htmltools)
library(base64enc)

# ignore the local if it confuses you
# only use it to delete the tempfile on exit
local({
  # make a tempfile to hold our chart  
  tf <- tempfile()
  # delete our tempfile on exit
  on.exit(unlink(tf))
  
  # save our chart as a big png; exaggerate the width
  png( tf, height = 800, width = 1600 )
    # make a kind of pretty chart
    plot(sin(0:90),cos(seq(0,360,by=4)),type="l", col= topo.colors(4))
    lines(sin(0:90),cos(0:90),type="l",col=topo.colors(4)[3])
  dev.off()
  
  intense(
    tags$img(
      style="height:200px;"
      ,src = dataURI(file=tf,mime="image/png")
    )
  )
})
```

### Example with Pairs to Show Auto

In the first example, we exaggerated the width so you could see how the image pans from right to left based on your mouse or touch movement.  `intense-images` automatically decides to pan.  To see how it adjusts resize your window when in full-screen display mode.

```{r "example_02"}
library(imageR)
library(htmltools)
library(base64enc)

# ignore the local if it confuses you
# only use it to delete the tempfile on exit
local({
  # make a tempfile to hold our chart  
  tf <- tempfile()
  # delete our tempfile on exit
  on.exit(unlink(tf))
  
  # save our chart as a big png; exaggerate the width
  png( tf, height = 1200, width = 1200 )
    # make a kind of pretty chart
    pairs(USJudgeRatings, main="Example from ?pairs")
  dev.off()
  
  intense(
    tags$img(
      style="height:400px;"
      ,src = dataURI(file=tf,mime="image/png")
    )
  )
})
```
